method

### 2022-06-09 06_Paper/ER-ED/method.Rmd
changed github repo

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[@Simmons2012].
The paradigm was written and presented using *PsychoPy*[@Peirce2019].
We used *R* with *R Studio*[@RCore2021; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CERED.
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CERED).

@@

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
<!-- Kommentar Denise: Die folgenden Sätze waren im Präteritum formuliert, ich hab es einfach umformuliert-->Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
It is followed by neutral or negative pictures for a total of 6 seconds.
After each block, participants retrospectively will rate their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.

@@

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CERED).

>>>>

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study[@Simmons2012].
The paradigm was written and presented using *PsychoPy*[@Peirce2019].
We used *R* with *R Studio*[@RCore2021; @RStudioTeam2020] with the main packages *afex*[@Singmann2021] and *BayesFactor*[@Morey2021] for all analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at https://github.com/ChScheffel/CAD.
A complete list of all measures assessed in the study can be found at OSF (<https://osf.io/vnj8x/>) and GitHub (https://github.com/ChScheffel/CAD).

@@

*Part one: ER task.* <br> Part one will be a standard ER task in a block design (see Figure \@ref(fig:DesignERED)), similar to paradigms previously used by our group[@Scheffel2021].
Participants will be told to actively view neutral and negative pictures (see [2.3.3](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing, and expressive suppression, respectively.
Every participant first will have the condition "active viewing-neutral" that serves as a baseline condition.
During this block, 20 neutral pictures will be presented.
Participants will be asked to "actively view all pictures and permit all emotions that may arise." 
In the second block, participants will actively view negative pictures.
During the third, fourth, and fifth block, participants will see negative pictures and will be asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants will be asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants will be asked to "take the position of a non-involved observer, thinking about the picture in a neutral way." 
Participants will be told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants will be told to "suppress their emotional facial expression." 
They should imagine being observed by a third person that should not be able to tell by looking at the facial expression whether the person is looking at an emotional picture.
Participants will be instructed not to suppress their thoughts or change their facial expression to the opposite[@Scheffel2021].
All participants will receive written instruction and complete a training session.
After the training session, participants will be asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) will be randomized between participants.
Each of the blocks consists of 20 trials showing neutral (Block 1) and negative (Blocks 2, 3, 4, 5) pictures.
Each trial begins with a fixation cross that lasts 3 to 5 seconds (random uniform distributed).
It is followed by neutral or negative pictures for a total of 6 seconds.
After each block, participants retrospectively will rate their subjective emotional arousal ("not at all aroused" to "very highly aroused"), their subjective effort ("not very exhausting" to "very exhausting"), and - after the ragulation blocks - the utility of the respective strategy ("not useful at all" to "very useful") on a continuous scale using a slider on screen.

@@

The paradigm code, as well as the R Markdown file used to analyze the data and write this document is available at our [Github repository](https://github.com/ChScheffel/CAD).
